Ecological network control

### 2018-06-18 paper/supp-info.Rmd
Figure was appearing before section title. Fixed that

```{r fig-assumption-sampling-nd, fig.height=fig_sizes()[[1]]/2, fig.width=fig_sizes()[[1]], fig.cap="Difference between the size of the minimum driver node set of the empirical network and the subsampled network. Lighter lines indicate the changes for each networks and the darker line indicates the overall trend."}
drake::loadd(fig_assumption_sampling)
fig_assumption_sampling[[1]]
```

>>>>

```{r fig-assumption-sampling-nd, fig.height=fig_sizes()[[1]]/2, fig.width=fig_sizes()[[1]], fig.cap="Difference between the size of the minimum driver node set of the empirical network and the subsampled network. Lighter lines indicate the changes for each networks and the darker line indicates the overall trend.", fig.pos="p", fig.align='center'}
drake::loadd(fig_assumption_sampling)
fig_assumption_sampling[[1]]
```
